%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Software Testing Self Assessment}
\author{Matthew Davidson}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \maketitle
  \begin{enumerate}
    \item Analyse requirements to determine appropriate testing strategies. \textbf{Mark: 4} 
      \begin{enumerate}
        \item Range of requirements, functional requirements, measurable quality attributes, qualitative requirements. \textbf{Mark: 4}
        \item Level of requirements, system, integration, unit. \textbf{Mark: 4}
        \item Identifying test approach for chosn attributes. \textbf{Mark: 3}
        \item Assess the appropriateness of your chose testing approach. \textbf{Mark: 3}
      \end{enumerate}
    \item Design and implement comprehensive test plans with instrumented code. \textbf{Mark: 4}
      \begin{enumerate}
        \item Construction of test plan. \textbf{Mark: 4}
        \item Evaluation of the quality of the test plan. \textbf{Mark: 2}
        \item Instrumentation of the code. \textbf{Mark: 5}
        \item Evaluation of the instrumentation. \textbf{Mark: 2}
      \end{enumerate}
    \item Apply a wide variety of testing techniques and compute test coverage and yield according to a variety of criteria. \textbf{Mark: 5}
      \begin{enumerate}
        \item Range of techniques. \textbf{Mark: 3}
        \item Evaluation criteria for the adequacy of the testing. \textbf{Mark: 4}
        \item Results of testing. \textbf{Mark: 5}
        \item Evaluation of the results. \textbf{Mark: 3}
      \end{enumerate}
    \item Evaluate the limitations of a given testing process, using statistical methods where appropriate and summarise outcomes. \textbf{Mark: 3}
      \begin{enumerate}
        \item Identifying gaps and omission in the testing process. \textbf{Mark: 4}
        \item Identifying target coverage/performance levels for the different testing procedures. \textbf{Mark: 3}
        \item Discussing how the testing carried out compares with the target levels. \textbf{Mark: 4}
        \item Discussion of what would be necessary to achieve the target levels. \textbf{Mark: 3}
      \end{enumerate}
    \item Conduct reviews and inspection and design and implement automated testing processes. \textbf{Mark: 4}
      \begin{enumerate}
        \item Identify and apply review criteria to selected parts of the code and identify issues in the code. \textbf{Mark: 3}
        \item Construct an appropriate CI pipeline for the software. \textbf{Mark: 5}
        \item Automate some aspects of the testing. \textbf{Mark: 4}
        \item Demonstrate the CI pipeline functions as expected. \textbf{Mark: 4}
      \end{enumerate}
  \end{enumerate}
\end{document}
